\documentclass[margin]{res}
\pdfmapfile{=fontawesome.map}

\usepackage{libertine}
%\usepackage{palatino}
%\usepackage[sfdefault]{gillius2}
\usepackage{microtype}
\usepackage{graphicx}
%\usepackage{fontspec}
\usepackage{fontawesome}

%\usepackage[strict]{changepage}
\usepackage{multirow}
\usepackage{fancyhdr}
%\usepackage{lastpage}
\usepackage{hyperref}

%\usepackage{geometry}
%\geometry{letterpaper,tmargin=0.2in,bmargin=0.6in,lmargin=1in,rmargin=1in}
\topmargin -.75in
\textheight 10.15in

\pagestyle{fancy}
\pagenumbering{gobble}
%no line at top
\renewcommand{\headrulewidth}{0pt}
\rfoot{\small{\today}}

%%%% Fonts  %%%%
%\font\helv=phvr at 10pt
%\font\bighelv=phvr at 24pt
\font\helv=GilliusADFNo2-Regular-lf-t1 at 10pt
\font\bighelv=GilliusADFNo2-Regular-lf-t1 at 22pt
% override \sectionfont from res.cls
\def\sectionfont{\helv}

%%%% List formatting  %%%%
\parskip=0in

\setlist{itemsep=0.01in, parsep=0.0in, topsep=0in, partopsep=-0.0in, leftmargin=0.1in} 

\setlist[itemize,1]{label=$\circ$, after=\vspace{-0.15in}}
\setlist[itemize,2]{label=$\bullet$, itemsep=0in, parsep=0in, partopsep=0in, after=\vspace{0.015in}}


\def\tightlist{}

% based on https://stackoverflow.com/a/3951837/1175053
\makeatletter% since we're using a macro containing @
\newcommand{\addspaces}[1]{%
  \@tfor\letter:=#1\do{%
    \letter\space
  }%
}
\makeatother% resets @ to its original meaning


\begin{document}
	\begin{tabular}{ll}
            \multirow{ 2}{*}{\bighelv \addspaces{Chan-Ho}\quad \addspaces{Suh}\qquad}
		&\helv csuh.web@gmail.com \\
		&\helv xxx - xxx - xxxx \\
		&\helv New York, New York  \\
		&\helv \faGithub \phantom{.} \faLinkedin \phantom{..} chanhosuh \\
	\end{tabular}

\vspace{-0.2in}

\begin{resume}
\vspace{-0.2cm}
\section{\helv Education}
\begin{list1}
\item {\bf BA}, {\helv Cornell University}, cum laude in mathematics,  May 2001
\item {\bf PhD}, {\helv University of California at Davis}, mathematics,  Dec 2007
\item {\bf MS}, {\helv Rutgers}, mathematical finance, Jan 2014
\end{list1}
\vspace{-0.1in}
\section{\helv Employment\\ History}
\begin{list1}
\item {\bf MIO Partners}\\
2016 -current\quad {\it Quant developer for trading}\\[0.05cm]
$\bullet$ Build tools, mainly in Python, for research and trading in volatility derivatives. \\[0.05cm]
$\bullet$ Create daily charts for chief investment officer to identify trading opportunities. \\[0.05cm]
$\bullet$ Project manager/tech lead for web application used for signal generation\\[0.05cm]
$\bullet$ Gather volatility data from varied sources, while cleaning/maintaining data.
\vspace{0.1cm}
\item {\bf JP Morgan Chase}\\[0.05cm]
2015 - 2016\quad {\it Quant developer for regulatory capital}\\[0.05cm]
$\bullet$ Provide solutions for improved oversight of firm-wide capital adequacy processes. \\[0.05cm]
$\bullet$ Identify and resolve data quality issues for high-visibility regulatory policy vetting.\\[0.05cm]
$\bullet$ Rapid, iterative, full-stack development in proprietary Python-based environment (Athena), from server-side processes to event-driven GUI design.
\vspace{0.1cm}
\item {\bf Nomura }\\ 
2014 - 2015 \quad {\it Front office developer for electronic trading}\\[0.05cm]
$\bullet$ Created a low-latency order book generator that used Tibco Rendezvous to aggregate market-data and pricing and communicate with smart order router and GUI (Java/Linux). \\[0.05cm]
$\bullet$ Primary maintainer of  automated market-maker for USD swaps and swap futures.\\[0.05cm]
$\bullet$ Created a FIX trade feed from ION trading platform into trade management system.
\vspace{0.1cm}
\item {\bf Nomura}\\
2013 \quad {\it Intern on equities connectivity team}\\[0.05cm]
$\bullet$ Contributed to  on-schedule deployment of ECN gateway by building Java framework to systematically monitor and analyze latency from multiple protocols.\\[0.05cm]
$\bullet$ Ensured compatibility of team's Ant build process to firm's Maven build process by completing conversion on several projects and documenting the conversion.
\\[-0.3cm]
\item {\bf University of California, Davis}\\
2012\qquad Lecturer\\
{\it Head instructor for courses in calculus, linear algebra, and probability}\vspace{0.05cm}
\item {\bf Bard College}, BHSEC program\\
2009 - 2011\qquad Assistant Professor\\
{\it Oversaw the development of accelerated math curriculum for early college program.}\vspace{0.05cm}
\item {\bf University of Victoria}\\
2008 - 2009\qquad PIMS Postdoctoral Fellow\\
{\it Conducted mathematical research in low-dimensional topology}
\end{list1}
\vspace{-0.15in}

\section{\helv Skills \&\\ Abilities}
\begin{list1}
\item Ability to self-manage and rapidly iterate while gathering and updating requirements.
\item Programming languages: {\helv Python}, { \helv Java}, {\helv C}
\item Work experience in a Linux server environment, using Unix tools (grep, awk, sed, vi(m), etc.)
\item Ability to digest new quantitative literature from a top-down, conceptual viewpoint
\end{list1}

\section{Education}\label{education}

\begin{itemize}
\tightlist
\item
  \textbf{BA}, Cornell University, cum laude in mathematics, May 2001
\item
  \textbf{PhD}, University of California at Davis, mathematics, Dec 2007
\item
  \textbf{MS}, Rutgers, mathematical finance, Jan 2014
\end{itemize}

\section{\texorpdfstring{Employment\\
History}{Employment History}}\label{employment-history}

\begin{itemize}
\item
  \textbf{LoanStreet Inc.}\\
  2018 - current, \emph{Software engineer for financial technology firm}

  \begin{itemize}
  \tightlist
  \item
    Rebuild Django backend, following OOP best practices to ensure
    accuracy, extensibility, and scaleability.
  \end{itemize}
\item
  \textbf{MIO Partners} (McKinsey \& Co subsidiary)\\
  2016 - 2018, \emph{Quant developer for trading}

  \begin{itemize}
  \tightlist
  \item
    Designed Python-based portfolio management tools following
    object-oriented principles. Tools are used interactively for
    analysis and as components in report-generation processes deployed
    in Docker containers.
  \item
    Created and maintained daily trading opportunity charts reviewed by
    the CEO. Data was processed from a variety of sources including
    emails and databases.
  \item
    As project manager, gathered requirements for a web app (React JS
    and Python), coded back-end computations, and managed two front-end
    developers.
  \end{itemize}
\item
  \textbf{JP Morgan Chase}\\
  2015 - 2016, \emph{Quant developer for regulatory capital}

  \begin{itemize}
  \tightlist
  \item
    Automated Excel and Access-based manual processes as robust server
    processes using proprietary Python-based environment (Athena).
  \item
    Worked on back-end processes and event-driven GUI design, following
    the Agile methodology, including thorough test coverage.
  \item
    Frequent communication and signoffs from business users were
    required, with careful documentation showing accuracy of results.
  \end{itemize}
\item
  \textbf{Nomura}\\
  2014 - 2015, \emph{Front office developer for electronic trading}

  \begin{itemize}
  \tightlist
  \item
    Created a low-latency order book generator that used Tibco
    Rendezvous to aggregate market-data and pricing and communicate with
    smart order router and GUI (Java/Linux).
  \item
    Primary maintainer of automated market-maker for USD swaps and swap
    futures.
  \item
    Created a FIX trade feed from ION trading platform into trade
    management system.
  \end{itemize}
\item
  \textbf{Nomura}\\
  2013, \emph{Intern for equities connectivity team}
\item
  \textbf{University of California, Davis}\\
  2012 Lecturer\\
  \emph{Head instructor for courses in calculus, linear algebra, and
  probability}
\item
  \textbf{Bard College}, BHSEC program\\
  2009 - 2011, Assistant Professor\\
  \emph{Oversaw the development of accelerated math curriculum for early
  college program.}
\item
  \textbf{University of Victoria}\\
  2008 - 2009, PIMS Postdoctoral Fellow\\
  \emph{Conducted mathematical research in low-dimensional topology}
\end{itemize}

\section{Skills \& Abilities}\label{skills-abilities}

\begin{itemize}
\tightlist
\item
  Able to self-manage and rapidly iterate while gathering and updating
  requirements.
\item
  Programming languages: {Python}, {Java}, {C}
\item
  Work experience in a Linux server environment, using Unix tools (grep,
  awk, sed, vi(m), etc.)
\item
  Able to digest new quantitative literature from a top-down, conceptual
  viewpoint
\end{itemize}

\section{Papers}\label{papers}

\begin{itemize}
\tightlist
\item
  ``Boundary-Twisted Normal Form and the Number of Elementary Moves to
  Unknot'', \emph{New York J. Math} 18 (2012) 389-408.
\item
  ``The Unknotting Problem and Normal Surface Q-Theory'', \emph{Journal
  of Knot Theory and Its Ramifications}, accepted for publication
\end{itemize}

\section{Fellowships \& Scholarships}\label{fellowships-scholarships}

\begin{itemize}
\tightlist
\item
  Pacific Institute for the Mathematical Sciences Postdoctoral
  Fellowship
\item
  National Science Foundation VIGRE Fellowship (4 years)
\item
  Rutgers MSMF Gary Chropuvka Scholarship Award
\end{itemize}

\section{Personal}\label{personal}

\begin{itemize}
\tightlist
\item
  Naturalized U.S. Citizen; moved to the U.S. at age eight.
\end{itemize}

\end{resume}
\end{document}




